\documentclass[10pt,letterpaper]{article}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=0.55in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{array}
\usepackage{tabularx}
\usepackage{fontawesome5}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=*, itemsep=2.1pt, topsep=2.1pt, parsep=0pt, partopsep=0pt}
\titleformat{\section}{\normalsize\bfseries}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{7.4pt}{3.8pt}
\renewcommand{\arraystretch}{1.09}

\newcommand{\resumeRole}[4]{
  \textbf{#1} \hfill #2\\
  \textit{#3} \hfill #4
}

\newcommand{\resumeCompactRole}[3]{
  \textbf{#1} \hfill #2\\
  \textit{#3}
}

\begin{document}
\fontsize{9.25}{11.05}\selectfont

\begin{center}
  {\Large \textbf{Frank Valdez}}\\[1.5pt]
  \faMapMarker*~Amityville, NY \quad | \quad \faPhone*~(516) 448-5064 \quad | \quad \faEnvelope~\href{mailto:frankiejvaldez@gmail.com}{frankiejvaldez@gmail.com}\\[1pt]
  \faLinkedin~\href{https://linkedin.com/in/frankiejvaldez}{linkedin.com/in/frankiejvaldez} \quad | \quad \faGithub~\href{https://github.com/frankstop}{github.com/frankstop}
\end{center}

\section*{Summary}
Software developer with recent production IT ownership and shipped projects in automation, data pipelines, public dashboards, and developer tooling. Strong in Python, TypeScript, SQL, REST APIs, GitHub Actions, and browser-based delivery; able to debug legacy operations, model messy data, and turn repeat work into maintained tools.

\section*{Technical Skills}
\begin{tabularx}{\textwidth}{@{}>{\bfseries}p{1.15in} >{\raggedright\arraybackslash}X@{}}
Languages & Python, TypeScript, JavaScript, C\#, SQL, Java, C++, Bash, PowerShell\\
Backend & FastAPI, Pydantic, SQLAlchemy, REST APIs, service integrations, API-backed applications\\
Frontend & React, Vite, Next.js, HTML, CSS, responsive UI, browser automation, WordPress automation\\
Data/DB & SQL Server, SSMS, SQLite, PostgreSQL, pandas, NumPy, scikit-learn, XGBoost, Jupyter\\
Automation & GitHub Actions CI/CD, GitHub CLI, shell scripting, Playwright, scraping, scheduled pipelines\\
\end{tabularx}

\section*{Experience}
\resumeRole{Gala Fresh Farms Supermarkets}{New York, NY}{IT Operations Manager}{Nov. 2025 -- Present}
\begin{itemize}
  \item Own daily SQL/SSMS workflows for a 70,000-record operational database, using joins, validation queries, update scripts, and data transformations to keep store data usable.
  \item Built dashboards and WordPress automation for batch deletion monitoring, weekly circular publishing, and local-to-live deployment workflows.
  \item Support legacy LOC SMS POS and back-office systems across 2 store locations, resolving database, workflow, payment, and user-reported production issues.
  \item Validate POS/payment behavior for WIC, EBT, credit card, and related tender workflows against store operations and data integrity requirements.
  \item Reconciled 14,000 active SKUs before batch deletion and added safeguards to avoid removing new or scalable inventory records.
\end{itemize}

\resumeRole{Wells Fargo (Contract)}{Des Moines, IA}{IT Operations Analyst}{Jun. 2023 -- Jul. 2023}
\begin{itemize}
  \item Validated provisioning workflows for 600 weekly shipments, enforcing 48-hour SLA and zero-defect delivery standards.
\end{itemize}

\resumeRole{LCS (Contract)}{Des Moines, IA}{Desktop Support Specialist}{Dec. 2022 -- Mar. 2023}
\begin{itemize}
  \item Supported migration of 22,000 employee profiles into Okta and resolved 70 daily support requests across access, login, and escalation workflows.
\end{itemize}

\resumeRole{John Deere (Contract)}{Des Moines, IA}{Traveling Infrastructure Engineer}{Jun. 2022 -- Dec. 2022}
\begin{itemize}
  \item Served as frontline infrastructure contact across 3 enterprise environments, documenting issues and coordinating fixes with senior engineers.
\end{itemize}

\resumeCompactRole{Earlier IT Support}{2014 -- 2022}{Help Desk, Account Management \& IT Support}
Wright Service Corp help desk support; Edge Realty Group account management and IT support across remote desktop, file server, onboarding, and business-user workflows.

\section*{Projects}
\textbf{f-ast} \hfill \href{https://github.com/frankstop/f-ast}{github.com/frankstop/f-ast}
\begin{itemize}
  \item Built a TypeScript parser toolkit that converts legacy Java 6--8 and C\# 5--7 codebases into compact structure, symbol, flow, and diagnostic output for AI-assisted code analysis.
\end{itemize}

\textbf{Civil Service Watch} \hfill \href{https://github.com/frankstop/civil-service-watch}{github.com/frankstop/civil-service-watch}
\begin{itemize}
  \item Built a scheduled Python monitor for public-sector exam and hiring pages, with change detection, source-health reporting, GitHub Actions refreshes, and a GitHub Pages dashboard.
\end{itemize}

\textbf{KingKullenResearch} \hfill \href{https://github.com/frankstop/KingKullenResearch}{github.com/frankstop/KingKullenResearch}
\begin{itemize}
  \item Built a weekly grocery-pricing pipeline from Freshop API data, adding longitudinal price tracking, reconciliation checks, predictive modeling, and GitHub Pages reporting.
\end{itemize}

\section*{Education}
\textbf{SUNY Old Westbury} \hfill Jan. 2024 -- Aug. 2025\\
B.S. Computer \& Information Sciences, GPA 3.85; Dean's List; Coding Club Re-Founder; Othello AI FastAPI capstone\\
\textbf{Nassau Community College} \hfill 2015 -- 2017\\
Associate of Science (A.S.)\\
\textbf{Certifications:} Google UX Design Certificate; Google IT Support Certificate

\end{document}
